### 2022-10-26 types.tex
things are hanging together ok, but it seems likely they're not possible to do in Rust? Unclear.

    {\inferrule{A : in(dₐ' ▷ dₐ''), A : out(dₐ ▷ dₐ''),… ⊢ p
    \\ dₐ' ∈ \{A ▷ dₐ'', dₐ ▷ dₐ''\}
    \\ (A : τₐ,… ⊢ dₐ ▷ dₐ'' : τₐ)…
    }
      {⊢ "declare"~A…~"in"~p}}

@@

    {\inferrule[varref-out]{}{A:out(d);d ⊢ A}}

    {\inferrule[varref-out-approx]{}{A:out(d'.d);B.d ⊢ A}}\textit{\MPM{Is this sound? Or can it allow the paths to vary too much? I feel like probably the latter....}}

    {\inferrule[varref-in]{}{A:in(d) ⊢ A : d}}

@@

    {\inferrule[axoim-transform]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d' : τ}{Γ ⊢ d : τ}}

@@

@@

{\inferrule[axoim-transform-base]{}{Γ ⊢ d ⇝ d'}}

\end{mathpar}    
    \caption{Types: axiom transformations }
    \label{fig:types3}
\end{figure}

@@

>>>>

    {\inferrule{A▷, dₐ▷A,… ⊢ p
    \\ (dₐ▷A : τₐ,… ⊢ dₐ : τₐ)…
    }
      {⊢ "declare"~A…~"in"~p}}

@@

    {\inferrule[varref-out]{}{ d▷A;d ⊢ A}}

%    {\inferrule[varref-out-approx]{}{A:out(d'.d);B.d ⊢ A}}\textit{\MPM{Is this sound? Or can it allow the paths to vary too much? I feel like probably the latter....}}

    {\inferrule[varref-in]{}{A▷ ⊢ A : A}}

@@

    {\inferrule[assert-matching]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d : τ}{Γ ⊢ d▷as(d')[0] : τ}}

@@

    {\inferrule[varref]{}{ d▷A : τ ⊢ A : τ}}

@@

{\inferrule[axoim-transform-abstract]{Γ,dₐ▷A : τₐ ⊢ d ⇝ d' \\ A~\fresh}{Γ ⊢ d[A/dₐ] ⇝ d'}}

{\inferrule[axoim-transform-concretize]{τₐ <: τ}{Γ,dₐ▷A : τₐ ⊢ d ⇝ d["?s"~τ/dₐ]}}

{\inferrule[axoim-transform-transitive]{Γ ⊢ d ⇝ d' \\ Γ ⊢ d' ⇝ d''}{
Γ ⊢ d ⇝ d''}}

{\inferrule[axoim-transform-unfold]{}{Γ,dₐ▷A : τₐ  ⊢ d ⇝ d[A/dₐ]}}

{\inferrule[axoim-transform-fold]{}{Γ,dₐ▷A : τₐ  ⊢ d[A/dₐ] ⇝ d}}

{\inferrule[axoim-transform-reflexive]{}{Γ ⊢ d ⇝ d}}

\end{mathpar}    
    \caption{Types: axiom transformations }
    \label{fig:axiom-types}
\end{figure}

@@

A new concern: we're building out the axiom transformation system in figure \ref{fig:axiom-types}, which relies on these substitution operators. I'm really not sure how to encode the substitutions---or the notion of an environment into which substitutions occur at all---into Rust. I guess they'd be... literal variables? Very unclear.
